IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/retrofit.tex

To get a feeling for how these operational semantics operate, we
describe a few sample programs, and their corresponding outputs.

\paragraph{Sending mutable references}  As each task maintains its own
global state for the target language, one might reasonably wonder what would
happen if you attempted to send a reference to another task.
\begin{align*}
    & |let i = TI (sandbox (brecvf x i' (IT (!(TI x)))))| \\
    & |in TI (send (IT (ref true)))|
\end{align*}
It would be a violation of information flow if such an operation actually
resulted in references being shared between two tasks.  In fact, the address
will be received by the sandboxed task, but it will be a dangling pointer; the
task will become stuck and removed from execution by \textsc{I-noStep}.  Readers
who are curious whether or not a static discipline could be enforced to
prevent these dangling pointers should check Section~\ref{sec:extensions}.

\paragraph{Status of the heap after a sandbox}  Here is a program whose
semantics depends on the definition of |klone|:
\begin{align*}
    & |let x = ref true| \\
    & |in TI (sandbox (IT (!x; !x))); x := false|
\end{align*}
When |klone| is the identity, the sandboxed task successfully dereferences
the contents of the reference to be true twice (recall that references
are cloned into the new global state).  When $\kappa$ is the constant function
to the empty store, $x$ becomes a dangling pionter.

\paragraph{Exceptions}  One language feature that has caused difficulty
for many information flow control systems is handling
exceptions~\cite{Hritcu:2013:YIB:2497621.2498098}.  The key difficulty
appears when an exception must cross a stack boundary where the current
label reverts back, i.e. across a |toLabeled| operator~\cite{lio}.
If the exception crosses this boundary, it can leak information about the
inner sensitive computation.

>>>>

To get a feeling for how these operational semantics operate, we
describe a few sample programs, and their corresponding behavior.

\paragraph{Sending mutable references}  As each task maintains its own
global state for the target language, one might reasonably wonder what would
happen if you attempted to send a reference to another task.
\begin{align*}
    & |let i = TI (sandbox (brecvf x i' (IT (!(TI x)))))|\\
    & |in TI (send (IT i) getLabel (IT (ref true)))|
\end{align*}
It would be a violation of information flow if such an operation actually
resulted in references being shared between two tasks.  In fact, the address
will be received by the sandboxed task, but it will be a dangling pointer; the
task will get stuck (under the |roundrobinf| scheduler the \textsc{I-noStep} will in turn remove it from the task list).  Readers
who are curious whether or not a static discipline could be enforced to
prevent these dangling pointers should check Section~\ref{sec:extensions}.

\paragraph{Status of the heap after a sandbox}  Consider a program whose
semantics depends on the definition of |klone|:
\begin{align*}
    & |let x = ref true| \\
    & |in TI (sandbox (IT (!x; !x))); x := false|
\end{align*}
When |klone| is the identity, the sandboxed task successfully dereferences
the contents of the reference to be |true| twice (recall that references
are cloned into the new global state).  When |klone| is the constant function
to the empty store, |x| is a dangling pointer.

\paragraph{Exceptions}  One language feature that has caused difficulty for
many information flow control systems is handling exceptions.
%
The key difficulty appears when considering the propagation of exceptions
across stack boundaries where the current label is restored, e.g., from secret
to public, as done by LIO's |toLabeled| and Breeze's
brackets~\cite{Hritcu:2013:YIB:2497621.2498098, stefan:2012:arxiv-flexible}.
%
If the exception crosses this boundary, it can leak information about the
inner secret computation into a public computation.
